% Made in Overleaf
% Base Resume Nov 2026
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage[margin=1.4cm]{geometry}
\usepackage{xcolor}


\urlstyle{same}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.0pt}


\addtolength{\oddsidemargin}{-0.15in}
\addtolength{\textwidth}{0.3in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-0pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small{#2}\\
    \end{tabular*}\vspace{-7pt}
}


\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}\vspace{0pt}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Large \scshape Aayan Ahmed} \\[2mm]
    \footnotesize \raisebox{-0.1\height}
    \faPhone\ \underline{(403) 708-0861} ~ 
    {\faEnvelope\ \underline{aayanahmed040@gmail.com}} ~ 
    {\faLinkedin\ \underline{\href{https://www.linkedin.com/in/aayan-ahmed-a10bab349/}{linkedin.com/in/aayan-ahmed-a10bab349/}}}  ~
    {\faGithub\ \underline{\href{https://github.com/AayanAhmed040}{github.com/AayanAhmed040}}}\\[1mm]
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education} \\[1mm]
  \resumeSubHeadingListStart
    \resumeSubheading
      {Mount Royal University}{Expected Graduation: May 2029}
      {Bachelor of Science | Major in Data Science}{Calgary, AB}
  \resumeSubHeadingListEnd
    \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework}: 
          Data Science I, 
          Problem Solving \& Programming (Python), 
          Mathematical Statistics, 
          Linear Algebra, 
          Calculus I
        }
    \resumeItemListEnd
    \vspace{-12pt}

    
%-----------SUMMARY OF QUALIFICATIONS-----------
\section{Summary of Qualifications}
    \vspace{-20pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {}{}
        \resumeItemListStart
            \resumeItem{Data Science undergraduate proficient in \textbf{Python}, \textbf{SQL}, and \textbf{Applied ML} logic (OpenCV, MediaPipe).}
            \resumeItem{Proven ability to engineer scalable solutions, including a \textbf{custom Python bot ecosystem} sold to multiple clients.}
            \resumeItem{Strong technical communicator with experience mentoring students in Python debugging and logic at Steamoji.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
    \vspace{-15pt}
    
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{     
     \textbf{Languages}{: Python, Java, SQL, JavaScript} \\[1mm]
     \textbf{Libraries/Frameworks}{: Pandas, NumPy, OpenCV, MediaPipe} \\[1mm]
     \textbf{Tools}{: Git, GitHub, VS Code, REST APIs, JSON, Data Pipelines, Linux/Bash}
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------PROJECTS-----------
\section{Projects} 
    \vspace{-5pt}
    \resumeSubHeadingListStart

    %PROJECT 1: Face Tracking App
    \resumeProjectHeading
        {\textbf{AI/ML Face-Tracking GIF Application} $|$ \href{https://github.com/AayanAhmed040/Face-Tracking-App}{github.com/AayanAhmed040/Face-Tracking-App}}
        {\textbf{Nov 2025}}
        \resumeItemListStart
            \resumeItem{Developed a real-time computer vision application using \textbf{Python}, \textbf{OpenCV}, and \textbf{MediaPipe}.}
            \resumeItem{Engineered facial landmark detection logic to track user head pose and expressions to trigger dynamic GIF overlays.}
            \resumeItem{Optimized frame processing loop to ensure low-latency performance during real-time video capture.}
        \resumeItemListEnd
    \vspace{-10pt}
        
    %PROJECT 2: Telegram Forwarder
    \resumeProjectHeading
        {\textbf{Telegram-to-Discord Data Pipeline} $|$ \href{https://github.com/AayanAhmed040/Telegram-Discord-Forwarder}{github.com/AayanAhmed040/Telegram-Discord-Forwarder}}
        {\textbf{Feb 2025}}
        \resumeItemListStart
            \resumeItem{Engineered a cross-platform event pipeline in \textbf{Python} to scrape and forward messages from Telegram to Discord.}
            \resumeItem{Implemented asynchronous handling with \textbf{Telethon} to manage high-volume data streams without blocking.}
            \resumeItem{Designed a JSON-based configuration system to manage webhooks and channel mapping for scalability.}
        \resumeItemListEnd
    \vspace{-10pt}

    %PROJECT 3: Dashboard
    \resumeProjectHeading
        {\textbf{Live Data Dashboard} $|$ \href{https://github.com/AayanAhmed040/Dakboard-Type-Thing}{github.com/AayanAhmed040/Dakboard-Type-Thing}}
        {\textbf{Apr 2025}}
        \resumeItemListStart
            \resumeItem{Developed a personal visualization dashboard integrating live data from \textbf{CoinGecko} and \textbf{OpenWeather APIs}.}
            \resumeItem{Leveraged AI-assisted (LLM) coding workflows to accelerate frontend development (HTML/JS).}
        \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-15pt}
  
%Experience
\section{Work Experience}
    \resumeSubHeadingListStart

        %STEAMOJI EXPERIENCE
        \resumeSubheading{Facilitator}{Jan 2024 – May 2025}{Steamoji}{Calgary, AB}
        \resumeItemListStart
            \resumeItem{Instructed students (ages 5-14) in core programming concepts, including \textbf{Python} and Scratch.}
            \resumeItem{Explained complex programming logic and problem-solving strategies to students one-on-one, reinforcing video-based curriculum.}
            \resumeItem{Debugged and troubleshot student-written \textbf{Python} code, identifying errors in logic, syntax, and flow.}
            \resumeItem{Mentored students across multiple STEM disciplines, including 3D modelling and engineering principles, adapting explanations.}
            \resumeItem{Collaborated daily with a facilitator team to manage classroom logistics and communicate student progress clearly to parents and managers.}
        \resumeItemListEnd
    \vspace{-5pt}
        %FREELANCE EXPERIENCE
        \resumeSubheading{Freelance Python Developer}{Feb 2022 – Jun 2023}{Self-Employed}{Calgary, AB}
        \resumeItemListStart
            \resumeItem{Developed, deployed, and sold custom \textbf{Discord bots} to multiple clients.}
            \resumeItem{Automated key community management tasks, replacing manual client work and moderation.}
            \resumeItem{Engineered user activity tracking systems and economy modules (JSON storage) to drive community engagement.}
            \resumeItem{Managed the full software life-cycle, from requirements gathering to deployment and long-term maintenance.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
    \vspace{-12pt}

\end{document}